NanoMaLy

### 2015-11-13 paper/pldi16-submission/main.tex
texing
operational semantics
texified proof sketch
s/nat/int/g
search loop
evaluation

%
% LaTeX template for prepartion of submissions to PLDI'15
%
% Requires temporary version of sigplanconf style file provided on
% PLDI'15 web site.
% 
\documentclass[pldi,indentedstyle=false]{sigplanconf-pldi15}

%
% the following standard packages may be helpful, but are not required
%
\usepackage{SIunits}            % typset units correctly
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

\section{Introduction}          % 1 page
\section{Overview}              % 2 pages?
\section{Type-carrying Semantics} % 2 pages
\begin{itemize}
\item values are tagged with their types, just like ``untyped'' langs
\item special ``hole'' value whose type is not yet known, used for function args
\item on-the-fly unification to determine ``correct'' type for holes
\end{itemize}

% Algorithm:
%   Input: ML Program (let f1 = e1 in let f2 = e2 in ... e)
%   Output: 'safe' or 'fn v1 .. vn' where 'fn v1 .. vn' gets stuck

\section{Evalution: Recasting Type Errors as Runtime Errors} % 1 page
\label{sec:eval-recast-type}
\begin{itemize}
\item benchmarks: our data + seminal data
\item both cases: \textbf{random} search sufficient to trigger runtime crash in 80\% of programs
\item how many of the ``safe'' programs are actually safe??
\end{itemize}

>>>>

%
% LaTeX template for prepartion of submissions to PLDI'15
%
% Requires temporary version of sigplanconf style file provided on
% PLDI'15 web site.
% 
\documentclass[10pt,pldi,indentedstyle=false]{sigplanconf-pldi15}

%
% the following standard packages may be helpful, but are not required
%
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{SIunits}            % typset units correctly
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI
\usepackage{xspace}
\usepackage{commands}

\usepackage{amsthm}
% \newtheorem{lemma}{Lemma}
% \newtheorem{corollary}{Corollary}
% \newtheorem{theorem}{Theorem}
% \newtheorem{definition}{Definition}
\theoremstyle{plain}% default 
\newtheorem{thm}{Theorem} % [section] 
\newtheorem{lem}[thm]{Lemma} 
\newtheorem{prop}[thm]{Proposition} 
\newtheorem*{cor}{Corollary} 
\theoremstyle{definition}
\newtheorem{defn}{Definition} % [section]

\usepackage[inference]{semantic}

\input{haskellListings}

@@

\section{Introduction}          % 1 page
\section{Overview}              % 2 pages?
% \section{Type-carrying Semantics} % 2 pages
\input{semantics.tex}

% \section{Evalution: Recasting Type Errors as Runtime Errors} % 1 page
\input{evaluation-witness.tex}
